---
title: "Instagram Data"
author: |-
  Estrella Hurtado
   Alina Valliani
date: "April 25, 2024"
output:
  html_document: default
---
## Introduction

Our data is derived from Instagram accounts and comes from the website known as Kaggle.com. 

Our data contains usernames, followings, followers, likes, comments, and locations of different accounts. 

We added some columns in our data such as engagement, engagement_quantile, post_timestamp, and caption_length. 

This data is interesting because it has a large sample of different accounts where we can draw conclusions about patterns in engagement scores. 
We also compare and contrast some things from our data. 

* A Link to the data https://www.kaggle.com/datasets/propriyam/instagram-data



## Problem Statement and Questions

We choose this data to understand Instagram engagement trends and the factors which contributes to post and videos. 

* What trends do we see based on posts with the highest engagement? 
* When do posts get the most engagement?
* What is the relationship between caption length and engagement?
* From pictures, carousel, and videos which one get the most highest engagement? 
* From pictures and videos which one get the most comments and likes? 


## What Libraries did we use?


```{r setup, include=TRUE,message=FALSE,echo=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE)
library(tidyverse)
library(lubridate)
library(stringr)
library(dplyr)
library(plotly)
```

* library(tidyverse)  Use to filter the data. 

* library(lubridate)  Use to format dates.

* library(stringr) Use to provides a set of functions designed to make work with strings.

* library(dplyr) Use to provide a function for each basic verb of data manipulation.

* library(plotly) Use to make interactive graphs. 


## Lets take a look at Unfiltered Data

```{r}
insta_data <- read_csv("instagram_data.csv")
glimpse(insta_data)
```



## Mutated Columns


### Key terms 

**Engagement**
- refers to the actual score from the data. 

**engagement_quantile**
- refers to the follower count divided into four different quarters. 

**post_timestamp**
- refers to the time when pictures or videos was posted. 

**caption_length**
- refers to the length of the caption. 


(Added new columns which represent 1 as the lowest followers, 2 and 3 as the average followers and the 4 as the highest followers). 


```{r}
new_data<- insta_data %>% mutate(engagement = round((((likes+comments)/followers)*100),digits = 2),
                                 follower_quantile = ntile(followers,4),
                                 engagement_quantile = ntile(engagement,4),
                                 post_timestamp = as_datetime(created_at),
                                 post_time = format(round(post_timestamp,units = "hours"),format = "%H:%M"),
                                 caption_length = lengths(strsplit(caption, ' ')))

```



## Filtered Data  

Our original data was messed up so we added new columns with calculated values. 

```{r,echo=FALSE}
glimpse(new_data)
```


## Key terms

**is_video**
- refers to the videos posted on Instagram account. 

**caption** 
- refers to the titles on the Instagram posts.

**comments/likes** 
- refers to the followers response to the posts.

**created_at**
- refers to the coded time stamp of when the post was created.

**multiple_images**
- refers to the boolean of whether the post was a carousel or multiple image upload. 

**followers/following**
- refers to the users. 


## Reference of Account Followers Distribution 

Insights on the average follower distribution meaning 1 is the lowest, 4 is the highest. 

```{r,echo=FALSE}
new_data %>% group_by(follower_quantile) %>% summarise(follower_mean = format(round(mean(followers),0),big.mark=','))
```



## What trends do we see based on posts with the highest engagement? 


Low amount of followers have the highest engagement whereas high amount of followers have the lowest engagement. 


```{r,echo=FALSE}
new_data %>% filter(engagement != is.na(engagement)) %>% 
  group_by(follower_quantile) %>% summarise(avg_eng = mean(engagement)) %>% 
  ggplot(aes(x = follower_quantile,y = avg_eng)) +
  geom_line() + labs(x='Follower Count Quartile',y = 'Average Engagement')
```


## When do posts get the most engagement?

This is showing average engagement percent by post local time. 

```{r,echo=FALSE}
new_data %>% filter(engagement != is.na(engagement)) %>% group_by(post_time) %>% summarise(mean(engagement),n())
```


## Reference of the Post Engagement

We see the most engagement between the hours of 5am, 8am, 12pm, 1pm, 4pm and 5pm, during peak times of the day. 

```{r,echo=FALSE}
time_eng <- new_data %>% filter(engagement != is.na(engagement)) %>% group_by(post_time) %>% summarise(eng_mean = round(mean(engagement),1)) %>% 
  ggplot(aes(x = eng_mean,y = post_time,fill = as.factor(post_time))) +
  geom_col(stat = 'identity') +
  scale_x_continuous(labels = waiver()) +
  labs(y = 'Posting Time', x = "Avg Engagement %") +
  scale_fill_manual(values = c('05:00'="tomato",'08:00'="tomato",'12:00'="tomato",'13:00'="tomato",'16:00'="tomato",'17:00'="tomato"), guide = FALSE)

ggplotly(time_eng)
```


## What is the relationship between caption length and engagement?

Highest engagement posts include captions with lengths x & y. 

The graph shows that the short captions gains more engagement. 


```{r,echo=FALSE}
new_data %>% filter(engagement != is.na(engagement)) %>% 
  mutate(caption_bucket = case_when(caption_length < 50 ~"<50",caption_length >=50 & caption_length<100~"50-100",caption_length>=100 & caption_length < 150 ~ "100-150",caption_length>=150 & caption_length < 200 ~ "150-200",caption_length>=200 & caption_length < 250 ~ "200-250",caption_length>=250 & caption_length < 300 ~ "250-300",caption_length>=300 & caption_length < 350 ~ "300-350",caption_length > 350 ~"350+")) %>% group_by(caption_bucket) %>%
  summarise(avg_eng = mean(engagement)) %>% ggplot(aes(x = caption_bucket,y = avg_eng))+geom_point(size = 5) + labs(x = "Caption Length",y = "Average Engagement")+ scale_x_discrete(limits = c("<50","50-100","100-150","150-200","200-250","250-300","300-350","350+"))
```



## From pictures, carousel and videos which one get the most highest engagement? 

The graph clearly show that the single images get more engagement whereas, carousels get less. 


```{r,echo=FALSE}
new_data %>% filter(engagement != is.na(engagement)) %>% mutate(type = case_when(is_video == TRUE & multiple_images == FALSE ~"Video",
                                    is_video == FALSE & multiple_images == FALSE ~ "Picture",
                                    multiple_images == TRUE ~ "Carousel")) %>% 
  group_by(type) %>% summarise(avg_eng = mean(engagement)) %>% 
  ggplot(aes(x = type,y = avg_eng))+
  geom_col() + labs(x = 'Content Type',y = 'Average Engagement')
```


## From pictures and videos which one get the most comment and likes? 

We see pictures get more comments and likes than videos. 

```{r,echo=FALSE}
new_data %>% 
  ggplot(aes(x = likes, y = comments, group = is_video, color = is_video)) + geom_point() +scale_y_log10() + scale_x_log10() + scale_color_manual(name = "Type", labels = c("Picture", "Video"),values = c("blue","red"))
```


The following examples, give us glimpse of the one the videos with the highes engagement as well as an image post. 

Here we notice this account @therawtextures has 263,044 followers, at the time of the data extraction and was able to receive 909,788 like and 2,683 comments with a 346% engagement score!

<blockquote class="instagram-media" data-instgrm-captioned data-instgrm-permalink="https://www.instagram.com/reel/C2M1zVQh6zC/?utm_source=ig_embed&amp;utm_campaign=loading" data-instgrm-version="14" style=" background:#FFF; border:0; border-radius:3px; box-shadow:0 0 1px 0 rgba(0,0,0,0.5),0 1px 10px 0 rgba(0,0,0,0.15); margin: 1px; max-width:540px; min-width:326px; padding:0; width:99.375%; width:-webkit-calc(100% - 2px); width:calc(100% - 2px);"><div style="padding:16px;"> <a href="https://www.instagram.com/reel/C2M1zVQh6zC/?utm_source=ig_embed&amp;utm_campaign=loading" style=" background:#FFFFFF; line-height:0; padding:0 0; text-align:center; text-decoration:none; width:100%;" target="_blank"> <div style=" display: flex; flex-direction: row; align-items: center;"> <div style="background-color: #F4F4F4; border-radius: 50%; flex-grow: 0; height: 40px; margin-right: 14px; width: 40px;"></div> <div style="display: flex; flex-direction: column; flex-grow: 1; justify-content: center;"> <div style=" background-color: #F4F4F4; border-radius: 4px; flex-grow: 0; height: 14px; margin-bottom: 6px; width: 100px;"></div> <div style=" background-color: #F4F4F4; border-radius: 4px; flex-grow: 0; height: 14px; width: 60px;"></div></div></div><div style="padding: 19% 0;"></div> <div style="display:block; height:50px; margin:0 auto 12px; width:50px;"><svg width="50px" height="50px" viewBox="0 0 60 60" version="1.1" xmlns="https://www.w3.org/2000/svg" xmlns:xlink="https://www.w3.org/1999/xlink"><g stroke="none" stroke-width="1" fill="none" fill-rule="evenodd"><g transform="translate(-511.000000, -20.000000)" fill="#000000"><g><path d="M556.869,30.41 C554.814,30.41 553.148,32.076 553.148,34.131 C553.148,36.186 554.814,37.852 556.869,37.852 C558.924,37.852 560.59,36.186 560.59,34.131 C560.59,32.076 558.924,30.41 556.869,30.41 M541,60.657 C535.114,60.657 530.342,55.887 530.342,50 C530.342,44.114 535.114,39.342 541,39.342 C546.887,39.342 551.658,44.114 551.658,50 C551.658,55.887 546.887,60.657 541,60.657 M541,33.886 C532.1,33.886 524.886,41.1 524.886,50 C524.886,58.899 532.1,66.113 541,66.113 C549.9,66.113 557.115,58.899 557.115,50 C557.115,41.1 549.9,33.886 541,33.886 M565.378,62.101 C565.244,65.022 564.756,66.606 564.346,67.663 C563.803,69.06 563.154,70.057 562.106,71.106 C561.058,72.155 560.06,72.803 558.662,73.347 C557.607,73.757 556.021,74.244 553.102,74.378 C549.944,74.521 548.997,74.552 541,74.552 C533.003,74.552 532.056,74.521 528.898,74.378 C525.979,74.244 524.393,73.757 523.338,73.347 C521.94,72.803 520.942,72.155 519.894,71.106 C518.846,70.057 518.197,69.06 517.654,67.663 C517.244,66.606 516.755,65.022 516.623,62.101 C516.479,58.943 516.448,57.996 516.448,50 C516.448,42.003 516.479,41.056 516.623,37.899 C516.755,34.978 517.244,33.391 517.654,32.338 C518.197,30.938 518.846,29.942 519.894,28.894 C520.942,27.846 521.94,27.196 523.338,26.654 C524.393,26.244 525.979,25.756 528.898,25.623 C532.057,25.479 533.004,25.448 541,25.448 C548.997,25.448 549.943,25.479 553.102,25.623 C556.021,25.756 557.607,26.244 558.662,26.654 C560.06,27.196 561.058,27.846 562.106,28.894 C563.154,29.942 563.803,30.938 564.346,32.338 C564.756,33.391 565.244,34.978 565.378,37.899 C565.522,41.056 565.552,42.003 565.552,50 C565.552,57.996 565.522,58.943 565.378,62.101 M570.82,37.631 C570.674,34.438 570.167,32.258 569.425,30.349 C568.659,28.377 567.633,26.702 565.965,25.035 C564.297,23.368 562.623,22.342 560.652,21.575 C558.743,20.834 556.562,20.326 553.369,20.18 C550.169,20.033 549.148,20 541,20 C532.853,20 531.831,20.033 528.631,20.18 C525.438,20.326 523.257,20.834 521.349,21.575 C519.376,22.342 517.703,23.368 516.035,25.035 C514.368,26.702 513.342,28.377 512.574,30.349 C511.834,32.258 511.326,34.438 511.181,37.631 C511.035,40.831 511,41.851 511,50 C511,58.147 511.035,59.17 511.181,62.369 C511.326,65.562 511.834,67.743 512.574,69.651 C513.342,71.625 514.368,73.296 516.035,74.965 C517.703,76.634 519.376,77.658 521.349,78.425 C523.257,79.167 525.438,79.673 528.631,79.82 C531.831,79.965 532.853,80.001 541,80.001 C549.148,80.001 550.169,79.965 553.369,79.82 C556.562,79.673 558.743,79.167 560.652,78.425 C562.623,77.658 564.297,76.634 565.965,74.965 C567.633,73.296 568.659,71.625 569.425,69.651 C570.167,67.743 570.674,65.562 570.82,62.369 C570.966,59.17 571,58.147 571,50 C571,41.851 570.966,40.831 570.82,37.631"></path></g></g></g></svg></div><div style="padding-top: 8px;"> <div style=" color:#3897f0; font-family:Arial,sans-serif; font-size:14px; font-style:normal; font-weight:550; line-height:18px;">View this post on Instagram</div></div><div style="padding: 12.5% 0;"></div> <div style="display: flex; flex-direction: row; margin-bottom: 14px; align-items: center;"><div> <div style="background-color: #F4F4F4; border-radius: 50%; height: 12.5px; width: 12.5px; transform: translateX(0px) translateY(7px);"></div> <div style="background-color: #F4F4F4; height: 12.5px; transform: rotate(-45deg) translateX(3px) translateY(1px); width: 12.5px; flex-grow: 0; margin-right: 14px; margin-left: 2px;"></div> <div style="background-color: #F4F4F4; border-radius: 50%; height: 12.5px; width: 12.5px; transform: translateX(9px) translateY(-18px);"></div></div><div style="margin-left: 8px;"> <div style=" background-color: #F4F4F4; border-radius: 50%; flex-grow: 0; height: 20px; width: 20px;"></div> <div style=" width: 0; height: 0; border-top: 2px solid transparent; border-left: 6px solid #f4f4f4; border-bottom: 2px solid transparent; transform: translateX(16px) translateY(-4px) rotate(30deg)"></div></div><div style="margin-left: auto;"> <div style=" width: 0px; border-top: 8px solid #F4F4F4; border-right: 8px solid transparent; transform: translateY(16px);"></div> <div style=" background-color: #F4F4F4; flex-grow: 0; height: 12px; width: 16px; transform: translateY(-4px);"></div> <div style=" width: 0; height: 0; border-top: 8px solid #F4F4F4; border-left: 8px solid transparent; transform: translateY(-4px) translateX(8px);"></div></div></div> <div style="display: flex; flex-direction: column; flex-grow: 1; justify-content: center; margin-bottom: 24px;"> <div style=" background-color: #F4F4F4; border-radius: 4px; flex-grow: 0; height: 14px; margin-bottom: 6px; width: 224px;"></div> <div style=" background-color: #F4F4F4; border-radius: 4px; flex-grow: 0; height: 14px; width: 144px;"></div></div></a><p style=" color:#c9c8cd; font-family:Arial,sans-serif; font-size:14px; line-height:17px; margin-bottom:0; margin-top:8px; overflow:hidden; padding:8px 0 7px; text-align:center; text-overflow:ellipsis; white-space:nowrap;"><a href="https://www.instagrdata:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAACgAAAAkCAYAAAD7PHgWAAABBklEQVR4Xu2XMQrCQBBFBQvR6wgJHsEDpHVjBDvvoBhbI3bWCkZbFUyhFrYiEat0WgmC6AVkdQqbIVmWZAOi82C64b+/bDWZDEEQP4phTLMaa9d003bTGMgu1psF7JVGNzuWPdzs18GDz443rgrIcndXbvW8g1axGfZKo7P2eBXc+WB74a3FGXtiA1kwzfnpqTF7hL3SwDfAaz+BqvjkwYADe6WhglQwJlQwKVQwKakVTGOoYNL5z4JxwBlUMEwqAu9SwTCpCLxLBcOkIvCusoKT9/WFQ6OkIvCukoJwt5rO0sehUVIReBem6ng+OLBXmnKjn4PbGM5PeKnqgXIlo5vHXoL4Nl4ZYqbbEGA7+wAAAABJRU5ErkJggg==am.com/reel/C2M1zVQh6zC/?utm_source=ig_embed&amp;utm_campaign=loading" style=" color:#c9c8cd; font-family:Arial,sans-serif; font-size:14px; font-style:normal; font-weight:normal; line-height:17px; text-decoration:none;" target="_blank">A post shared by Priyanshu Kumar (@therawtextures)</a></p></div></blockquote> <script async src="//www.instagram.com/embed.js"></script>


Below is an example of a single image that gained @maaren_xx creator a 105% engagement score with 3,222 likes and 45 comments while having 3,114 followers. 

<blockquote class="instagram-media" data-instgrm-captioned data-instgrm-permalink="https://www.instagram.com/p/BlqOhLLlXFR/?utm_source=ig_embed&amp;utm_campaign=loading" data-instgrm-version="14" style=" background:#FFF; border:0; border-radius:3px; box-shadow:0 0 1px 0 rgba(0,0,0,0.5),0 1px 10px 0 rgba(0,0,0,0.15); margin: 1px; max-width:540px; min-width:326px; padding:0; width:99.375%; width:-webkit-calc(100% - 2px); width:calc(100% - 2px);"><div style="padding:16px;"> <a href="https://www.instagram.com/p/BlqOhLLlXFR/?utm_source=ig_embed&amp;utm_campaign=loading" style=" background:#FFFFFF; line-height:0; padding:0 0; text-align:center; text-decoration:none; width:100%;" target="_blank"> <div style=" display: flex; flex-direction: row; align-items: center;"> <div style="background-color: #F4F4F4; border-radius: 50%; flex-grow: 0; height: 40px; margin-right: 14px; width: 40px;"></div> <div style="display: flex; flex-direction: column; flex-grow: 1; justify-content: center;"> <div style=" background-color: #F4F4F4; border-radius: 4px; flex-grow: 0; height: 14px; margin-bottom: 6px; width: 100px;"></div> <div style=" background-color: #F4F4F4; border-radius: 4px; flex-grow: 0; height: 14px; width: 60px;"></div></div></div><div style="padding: 19% 0;"></div> <div style="display:block; height:50px; margin:0 auto 12px; width:50px;"><svg width="50px" height="50px" viewBox="0 0 60 60" version="1.1" xmlns="https://www.w3.org/2000/svg" xmlns:xlink="https://www.w3.org/1999/xlink"><g stroke="none" stroke-width="1" fill="none" fill-rule="evenodd"><g transform="translate(-511.000000, -20.000000)" fill="#000000"><g><path d="M556.869,30.41 C554.814,30.41 553.148,32.076 553.148,34.131 C553.148,36.186 554.814,37.852 556.869,37.852 C558.924,37.852 560.59,36.186 560.59,34.131 C560.59,32.076 558.924,30.41 556.869,30.41 M541,60.657 C535.114,60.657 530.342,55.887 530.342,50 C530.342,44.114 535.114,39.342 541,39.342 C546.887,39.342 551.658,44.114 551.658,50 C551.658,55.887 546.887,60.657 541,60.657 M541,33.886 C532.1,33.886 524.886,41.1 524.886,50 C524.886,58.899 532.1,66.113 541,66.113 C549.9,66.113 557.115,58.899 557.115,50 C557.115,41.1 549.9,33.886 541,33.886 M565.378,62.101 C565.244,65.022 564.756,66.606 564.346,67.663 C563.803,69.06 563.154,70.057 562.106,71.106 C561.058,72.155 560.06,72.803 558.662,73.347 C557.607,73.757 556.021,74.244 553.102,74.378 C549.944,74.521 548.997,74.552 541,74.552 C533.003,74.552 532.056,74.521 528.898,74.378 C525.979,74.244 524.393,73.757 523.338,73.347 C521.94,72.803 520.942,72.155 519.894,71.106 C518.846,70.057 518.197,69.06 517.654,67.663 C517.244,66.606 516.755,65.022 516.623,62.101 C516.479,58.943 516.448,57.996 516.448,50 C516.448,42.003 516.479,41.056 516.623,37.899 C516.755,34.978 517.244,33.391 517.654,32.338 C518.197,30.938 518.846,29.942 519.894,28.894 C520.942,27.846 521.94,27.196 523.338,26.654 C524.393,26.244 525.979,25.756 528.898,25.623 C532.057,25.479 533.004,25.448 541,25.448 C548.997,25.448 549.943,25.479 553.102,25.623 C556.021,25.756 557.607,26.244 558.662,26.654 C560.06,27.196 561.058,27.846 562.106,28.894 C563.154,29.942 563.803,30.938 564.346,32.338 C564.756,33.391 565.244,34.978 565.378,37.899 C565.522,41.056 565.552,42.003 565.552,50 C565.552,57.996 565.522,58.943 565.378,62.101 M570.82,37.631 C570.674,34.438 570.167,32.258 569.425,30.349 C568.659,28.377 567.633,26.702 565.965,25.035 C564.297,23.368 562.623,22.342 560.652,21.575 C558.743,20.834 556.562,20.326 553.369,20.18 C550.169,20.033 549.148,20 541,20 C532.853,20 531.831,20.033 528.631,20.18 C525.438,20.326 523.257,20.834 521.349,21.575 C519.376,22.342 517.703,23.368 516.035,25.035 C514.368,26.702 513.342,28.377 512.574,30.349 C511.834,32.258 511.326,34.438 511.181,37.631 C511.035,40.831 511,41.851 511,50 C511,58.147 511.035,59.17 511.181,62.369 C511.326,65.562 511.834,67.743 512.574,69.651 C513.342,71.625 514.368,73.296 516.035,74.965 C517.703,76.634 519.376,77.658 521.349,78.425 C523.257,79.167 525.438,79.673 528.631,79.82 C531.831,79.965 532.853,80.001 541,80.001 C549.148,80.001 550.169,79.965 553.369,79.82 C556.562,79.673 558.743,79.167 560.652,78.425 C562.623,77.658 564.297,76.634 565.965,74.965 C567.633,73.296 568.659,71.625 569.425,69.651 C570.167,67.743 570.674,65.562 570.82,62.369 C570.966,59.17 571,58.147 571,50 C571,41.851 570.966,40.831 570.82,37.631"></path></g></g></g></svg></div><div style="padding-top: 8px;"> <div style=" color:#3897f0; font-family:Arial,sans-serif; font-size:14px; font-style:normal; font-weight:550; line-height:18px;">View this post on Instagram</div></div><div style="padding: 12.5% 0;"></div> <div style="display: flex; flex-direction: row; margin-bottom: 14px; align-items: center;"><div> <div style="background-color: #F4F4F4; border-radius: 50%; height: 12.5px; width: 12.5px; transform: translateX(0px) translateY(7px);"></div> <div style="background-color: #F4F4F4; height: 12.5px; transform: rotate(-45deg) translateX(3px) translateY(1px); width: 12.5px; flex-grow: 0; margin-right: 14px; margin-left: 2px;"></div> <div style="background-color: #F4F4F4; border-radius: 50%; height: 12.5px; width: 12.5px; transform: translateX(9px) translateY(-18px);"></div></div><div style="margin-left: 8px;"> <div style=" background-color: #F4F4F4; border-radius: 50%; flex-grow: 0; height: 20px; width: 20px;"></div> <div style=" width: 0; height: 0; border-top: 2px solid transparent; border-left: 6px solid #f4f4f4; border-bottom: 2px solid transparent; transform: translateX(16px) translateY(-4px) rotate(30deg)"></div></div><div style="margin-left: auto;"> <div style=" width: 0px; border-top: 8px solid #F4F4F4; border-right: 8px solid transparent; transform: translateY(16px);"></div> <div style=" background-color: #F4F4F4; flex-grow: 0; height: 12px; width: 16px; transform: translateY(-4px);"></div> <div style=" width: 0; height: 0; border-top: 8px solid #F4F4F4; border-left: 8px solid transparent; transform: translateY(-4px) translateX(8px);"></div></div></div> <div style="display: flex; flex-direction: column; flex-grow: 1; justify-content: center; margin-bottom: 24px;"> <div style=" background-color: #F4F4F4; border-radius: 4px; flex-grow: 0; height: 14px; margin-bottom: 6px; width: 224px;"></div> <div style=" background-color: #F4F4F4; border-radius: 4px; flex-grow: 0; height: 14px; width: 144px;"></div></div></a><p style=" color:#c9c8cd; font-family:Arial,sans-serif; font-size:14px; line-height:17px; margin-bottom:0; margin-top:8px; overflow:hidden; padding:8px 0 7px; text-align:center; text-overflow:ellipsis; white-space:nowrap;"><a href="https://www.instagram.com/p/BlqOhLLlXFR/?utm_source=ig_embed&amp;utm_campaign=loading" style=" color:#c9c8cd; font-family:Arial,sans-serif; font-size:14px; font-style:normal; font-weight:normal; line-height:17px; text-decoration:none;" target="_blank">A post shared by Maren (@maaren_xx)</a></p></div></blockquote> <script async src="//www.instagram.com/embed.js"></script>

 

## Summary

In summary, our presentation emphasized that our Instragram accounts data have following: 

* Highest engagement posts have lowest followers. 

* Highest engagement posts happen between early morning, noon and afternoon hours. 

* Highest engagement posts have short captions. 

* Single images get more engagement than carousels and videos. 

* In general, Pictures get more engagement than videos.
