---
title: "Final Project - Instagram Data"
author: "Estrella Hurtado"
date: "2024-04-04"
output: html_document
---
Introduction
Where we got the data
What categories we used. (followers buckets, caption lengths, keyword buckets)


```{r setup, include=TRUE,message=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE)
library(tidyverse)
library(lubridate)
```

#Instagram Data Title Goes Here

```{r}
insta_data <- read_csv("instagram_data.csv")
glimpse(insta_data)
```

Create new columns with calculated values
```{r}
new_data<- insta_data %>% mutate(engagement = round((((likes+comments)/followers)*100),digits = 2),
                                 follower_quantile = ntile(followers,4),
                                 engagement_quantile = ntile(engagement,4),
                                 post_timestamp = as_datetime(created_at),
                                 post_time = format(round(post_timestamp,units = "hours"),format = "%H:%M"),caption_length = lengths(strsplit(caption, ' ')))
```

```{r}
glimpse(new_data)
```

When do posts get the most engagement?

We see the most engagement between the hours of 4PM and 9PM
```{r}
new_data %>% ggplot(aes(x = engagement,y = post_time, na.rm = T)) +geom_col() +
  scale_x_continuous(labels = waiver()) +
  labs(y = NULL, x = "Engagement")
```


Based on the highest engagement, what trends to we see?
density plot


```{r}
new_data %>% ggplot(aes(x = engagement)) +geom_histogram() +labs(y = NULL, x = "Engagement")
```


Relationship between string lengths and engagement
Highest engaments posts include captions with lenghts x & y
```{r}
new_data %>% filter(engagement_quantile==4) %>% ggplot(aes(x = engagement,y = caption_length,na.rm = T)) +geom_line() +
  labs(y = NULL, x = "Engagement")+ scale_y_log10() + scale_x_log10()
```


do pictures or videos get more engagement?
We see pictures get more engagement
```{r}
new_data %>% ggplot(aes(x = likes, y = comments, color = is_video)) + geom_point() +scale_y_log10() + scale_x_log10()
```



#what types of accounts have the most followers?
Count keywords in captions and categorize engagement
```{r}

```


