<<<<<<< HEAD
---
title: "Final Project - Instagram Data"
author: "Estrella Hurtado & Allina Valliani"
date: "2024-04-04"
output: html_document
---
## Introduction
Where we got the data
What categories we used. (followers buckets, caption lengths, keyword buckets)


```{r setup, include=TRUE,message=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE)
library(tidyverse)
library(lubridate)
library(stringr)
library(dplyr)
library(plotly)
```

## Imported Data

```{r}
insta_data <- read_csv("instagram_data.csv")
glimpse(insta_data)
```


# Mutated columns
Created new columns with calculated values
```{r}
new_data<- insta_data %>% mutate(engagement = round((((likes+comments)/followers)*100),digits = 2),
                                 follower_quantile = ntile(followers,4),
                                 engagement_quantile = ntile(engagement,4),
                                 post_timestamp = as_datetime(created_at),
                                 post_time = format(round(post_timestamp,units = "hours"),format = "%H:%M"),caption_length = lengths(strsplit(caption, ' ')))

```

## Mutated data glimpse  
```{r}
glimpse(new_data)
```
## Account Follower Distribution
Insights on the account follower distribution 1 is the lowest, 4 the highest
```{r}
new_data %>% group_by(follower_quantile) %>% summarise(follower_mean = format(round(mean(followers),0),big.mark=','))
```


## Instagram engagement trends

engagement vs. follower count bucket
```{r}
new_data %>%
  group_by(follower_quantile)%>%
  summarise(engagement)%>%
  ggplot(aes(x = follower_quantile,y = engagement,na.rm=T))+
  geom_line()

```

## Post time vs Engament

```{r}
new_data %>% filter(engagement != is.na(engagement)) %>% group_by(post_time) %>% summarise(mean(engagement),n())
```

> *When do posts get the most engagement?

We see the most engagement between the hours of 5AM, 8AM, 12 PM, 1 PM, 4PM and 5PM, During peak times of the day. This is showing avg engagement% by post local time

```{r}
time_eng <- new_data %>% filter(engagement != is.na(engagement)) %>% group_by(post_time) %>% summarise(eng_mean = round(mean(engagement),1)) %>% 
  ggplot(aes(x = eng_mean,y = post_time,fill = as.factor(post_time))) +
  geom_col(stat = 'identity') +
  scale_x_continuous(labels = waiver()) +
  labs(y = 'Posting Time', x = "Avg Engagement %") +
  scale_fill_manual(values = c('05:00'="tomato",'08:00'="tomato",'12:00'="tomato",'13:00'="tomato",'16:00'="tomato",'17:00'="tomato"), guide = FALSE)

ggplotly(time_eng)
```

##Relationship between caption lengths and engagement

Highest engagement posts include captions with lengths x & y
```{r}
new_data %>% filter(engagement != is.na(engagement)) %>% mutate(caption_bucket = case_when(caption_length < 100 ~"<100",
                              TRUE ~ "Other")) %>% group_by(caption_bucket) %>%
  summarise(avg_eng = round(mean(engagement),1),na.rm = T)
```

##Pictures/Videos/Carousel vs. Engagement

Do pictures or videos get more engagement?
Clearly single images get more engagement and carousels get less

```{r}
new_data %>% filter(engagement != is.na(engagement)) %>% mutate(type = case_when(is_video == TRUE & multiple_images == FALSE ~"Video",
                                    is_video == FALSE & multiple_images == FALSE ~ "Picture",
                                    multiple_images == TRUE ~ "Carousel")) %>% 
  group_by(type) %>% summarise(avg_eng = mean(engagement)) %>% 
  ggplot(aes(x = type,y = avg_eng))+
  geom_col()
```

We see pictures get more engagement
```{r}
new_data %>% 
  ggplot(aes(x = likes, y = comments, color = is_video)) + geom_point() +scale_y_log10() + scale_x_log10() + scale_fill_discrete(name = "Type", labels = c("Picture", "Video", "N/A"))
```

#what types of accounts have the most followers?
Count keywords in captions and categorize engagement
```{r}
terms <- c('travel','food','drink','trip','brunch','makeup','beauty','hair','tutorial','webinar','course','journalism','inform','vacation','photography','wildlife','cake','episode','artist','story','reel','carousel','video','halloween','valentine','christmas','climate','communities',' art ','nature','mountain','country','hills','book','home','car','weekend','dress','baby','gym','fitness','dogs',' cats',' cat ',' dog ','fashion','birthday','goal','adventure','new york','camera','#ad ','hotel','flight',' eat ','music','garden','health','wellness','winter','new year','holiday','outfit')

term_regex <- paste0('(',paste(terms,collapse ='|'),')')

keyword_addition <- new_data %>%
  mutate(caption = tolower(caption),keywordtag = sapply(str_extract_all(caption,term_regex),function(x)paste0(x,collapse = ',')))

summarise(keyword_addition,owner_username,caption,keywordtag)
```


```{r}
caption_catergories <- keyword_addition %>% mutate(case_when(keywordtag == "Travel"~"Travel"))
```

count of keywords used
engagement distribution for each keyword